Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-16 paper/paper.tex
Spelling correction.
Another spelling fix.

For each light source we imagine a rectangular pyramid with the region-of-interest of the shadow plane as its base and the light source as its vertex. (See figure \ref{fig:space_partitioning}). We divide the pyramid into chunks and to each chunk associate all the spheres with a center in the chunk. When checking if a line segment intersects any sphere, we can ignore any sphere not in a chunk near the line segment. In particular, we started by dividing the pyramid into four levels. At the top level there are no subdivisions as we would have to check the spheres in each division anyway. This is because any partition that gets arbitrarity close to the light source can include spheres that shadow the entire shadow plane. The next level down is divided into truncated pyramids. The top plane of this layer can be though of as divided into squares with a side length equal to $r$ the radius of the spheres. A ray of light from the source will pass through one of these squares on its way to the shadow plane unless it is blocked in the previous layer. In this second highest layer it can only be blocked by spheres whose centers are beneath that square or any adjacent square. Therefore, we check for intersection only with spheres that fall in these partitions. In python we implement this by finding the intersection of the light path with the top plane and calculating integer coordinates of the square in which the intersection falls. Then from this coordinate pair is calculated a list of adjacent coordinates. All of these pairs are used in turn to perform a look-up operation in a python dictionary object each of which results in a list of spheres. Only these spheres are checked for intersection. The levels beneath that one work the same way. The benefit to dividing the lower part of the pyramid further is that lower levels have a greater capacity to divide th spheres. As noted in the annotations on figure \ref{fig:space_partitioning}, a sphere can be sorted into a partition in a level higher than its center if it intersects the boundary between the layers. This is necessary because the part of the sphere above the plane dividing the levels might block a light path that does not go through an adjacent square. The problem is avoided by putting the sphere in the higher level. It might seem at first that this trick makes the method no longer a space-partioning method, but it fact it merely means that the partitions are not as drawn in figure \ref{fig:space_partitioning}. Instead the top and bottom of a partition is at a distance $r$ below the planes drawn in figure \ref{fig:space_partitioning} (With the exception of the top of the top partition and the bottoms of the bottom partitions).

>>>>

For each light source we imagine a rectangular pyramid with the region-of-interest of the shadow plane as its base and the light source as its vertex. (See figure \ref{fig:space_partitioning}). We divide the pyramid into chunks and to each chunk associate all the spheres with a center in the chunk. When checking if a line segment intersects any sphere, we can ignore any sphere not in a chunk near the line segment. In particular, we started by dividing the pyramid into four levels. At the top level there are no subdivisions as we would have to check the spheres in each division anyway. This is because any partition that gets arbitrarity close to the light source can include spheres that shadow the entire shadow plane. The next level down is divided into truncated pyramids. The top plane of this layer can be thought of as divided into squares with a side length equal to $r$ the radius of the spheres. A ray of light from the source will pass through one of these squares on its way to the shadow plane unless it is blocked in the previous layer. In this second highest layer it can only be blocked by spheres whose centers are beneath that square or any adjacent square. Therefore, we check for intersection only with spheres that fall in these partitions. In python we implement this by finding the intersection of the light path with the top plane and calculating integer coordinates of the square in which the intersection falls. Then from this coordinate pair is calculated a list of adjacent coordinates. All of these pairs are used in turn to perform a look-up operation in a python dictionary object each of which results in a list of spheres. Only these spheres are checked for intersection. The levels beneath that one work the same way. The benefit to dividing the lower part of the pyramid further is that lower levels have a greater capacity to divide the spheres. As noted in the annotations on figure \ref{fig:space_partitioning}, a sphere can be sorted into a partition in a level higher than its center if it intersects the boundary between the layers. This is necessary because the part of the sphere above the plane dividing the levels might block a light path that does not go through an adjacent square. The problem is avoided by putting the sphere in the higher level. It might seem at first that this trick makes the method no longer a space-partioning method, but it fact it merely means that the partitions are not as drawn in figure \ref{fig:space_partitioning}. Instead the top and bottom of a partition is at a distance $r$ below the planes drawn in figure \ref{fig:space_partitioning} (With the exception of the top of the top partition and the bottoms of the bottom partitions).
